### 2022-11-18 extension.rmd
add r1

---
title             : "Online appendix to \"Bayesian (comparative) journalism studies\""
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

@@

```{r setup, include = FALSE}
library("papaja")
require(brms)
import_brms <- readRDS("import_brms.RDS")
```

@@

## Expression of disaggregated out-level model in MASS

@@

# Validation of the seed dictionaries

@@

# Extensions to Example 1

>>>>

---
title             : "Online appendix to \"Bayesian multilevel modeling and its application in comparative communication research\""
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

@@

```{r setup, include = FALSE}
library("papaja")
require(brms)
require(parameters)
import_brms <- readRDS("import_brms.RDS")
```

@@

## Expression of disaggregated outlet-level model in MASS

@@

# Multivariate regression of Example 1

Source code:

```r
brm(mvbind(C9, C10) ~ EXPRNCE + RANK + GENDER + UNI_EDU + eiu + gdppc + (1|COUNTRY),
    family=cumulative("logit"), cores = 4, iter = 3000, sample_prior = TRUE,
    data = wjs, control = list(adapt_delta = 0.99), prior = informative_prior)
```

## Results

```{r, results = "asis", warning = FALSE, echo = FALSE}
clmod <- readRDS("ppa_clmod.RDS")
suppressWarnings(print(print_md(parameters(clmod, ci = 0.95))))
```

# Example 2: Validation of the seed dictionaries

@@

# Extensions to the useNews example
